MSE and dynamic state variable model with sigma function

### 2018-04-16 doc/MSE_MAR_18.tex
changes commented by skype

For purposes of model simplicity, we considered a hypothetical mixed fishery on two species. The fishery was modelled in a individual based dynamic state variable model. In order to allowed for fishing effort allocation, the model was seasonally (6 seasons) and spatially (areas A and B) explicit. The dynamics of the two fish species were governed by a simple age-structured model that is also seasonally and spatially explicit. The age structured model for the fish species was based on 4 cohorts, and individuals were assumed to be born at age 0, and in season 1. The number of fish $i$ of age $a$ at year $y$, in season $s$ and area $p$ was written as $N_i (a, y, s, p)$. The number of new-born individuals in the model was independent of the size of the adult population, but was function of area $p$ ($R_i (p)$). Numbers of recruits were set to 100 individuals during the first season, and spawning population of species 1 ocurred in area $A$, while species 2 did so in area B. Thus, individuals could be born in each of the areas, such that:  
\begin{equation}
N_i (0, y, 1, p) = R_i (p)
\end{equation}

Moreover, combining the weight-based von Bertalanffy growth equation ($L\infty= 20$, $k= 0.093$), with the age-weight relationship ($W= L\infty*(1-e^{-k*a})$); weight per fish was higher for the older fish. Mortality in the model could occur from catches in the fishery, and natural causes such as predation, diseases, and scenesens. However, for simplicity we assumed that his natural mortality was negligible. Althought such absence of natural mortality impossible in reality, one could argue that the model thus mimics long-lived species. The decrease in population numbers was thus the result of the catches ($C_i (a, y, s, p)$), which were in turn a function of age dependent catchability $q(a)$, and fishing effort $E (y,s,p)$ in any time, season, and area. 
\begin{equation}
C_i (a, y, s, p) = q(a) * E(y,s,p),
\end{equation}
and 
\begin{equation}
N_i (a, y, s, p) = N_i (a, y, s, p) - C (a, y, s, p). 
\end{equation}

It was assumed that fishing mortality ocurred before migration ocurred. Migration for each species was defined by a matrix $Mig$ that defines the impact of migration (.e. immigration-emigration) on a given stock was also dependent on the relative sizes of the stocks. The size of that matrix  was defined by the number of age classes, seasons and number of immigrants into area $p$ ($im$) and emigrants leaving area $p$ ($em$) in the model. A 20 \% constant migration during any season was set between areas. The migration in population numbers ($Mig (a, 1, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs.   
\begin{equation}
Mig (a, 1, s, im, em) = Mig(a, 1, s, im, em) + N (a, y, s, em) * P (a, y, s, i, em, im),
\end{equation}
and then population numbers
\begin{equation}
N (a, y, s, im) = N (a, y, s, im) +  Mig (a, 1, s, im, em).
\end{equation}

@@

To simulate the process of monitoring the stock, we developed models for state-dependent behaviour of individual fishing vessels, translated into behaviour of the fleet and implemented using stochastic dynamic programming \cite{Alzorriz2018, Batsleer2015, ClarkandMangel2000, Dowling2011, Houston1999, Poos2010}. A dynamic state variable model \cite{ClarkandMangel2000, Houston1999} was used to model location choice, extending the model structure in \cite{Batsleer2015}. In order to accommodate each individual vessels set of choices, the model may be constrained by individual vessels quota for the individual species and will respond by changing their fishing pattern in terms of: (i) whether or not to go fishing in one of the two areas ($A$ and $B$), and (ii) whether to discard one or more species and age class combinations. The model had annual fines for exceeding landings or catch quota as in \cite{Alzorriz2018}). In order to calculate state dependent choices during the year, we started by defining the annual fines for exceeding landings or catch quotas at the end of the year:
\begin{equation}
\Phi (C_i, Q_i, F_i)= -\sum_i (max( 0, (C_i - Q_i))* F_i),
\end{equation}
where $C_i$ was the cumulative annual landings or catches for species $i$ for an individual vessel. These cumulative landings defined the state of the individual. $Q_i$ was the annual individual quota for landings or catches for the quota species. Individual quotas were not transferable. In order to reduce computation time, we set quota only for two species. $F_i$ was the fine per unit weight for exceeding individual landings or catch quotas was set to $3 x 10^3$ Euro day\textsuperscript{-1}. These high fines combined with an assumed 100\% detection of exceeding quotas resulted in model results in which fishers comply with quota regulations.

The maximum expected utility between current season $s$ and the end of the year was $V (C_i, Q_i, F_i, s)$, and the model started by setting $V (C_i, Q_i, F_i, s)= \Phi (C_i, Q_i, F_i)$. For preceding seasons, the expected utility depended on individual choices, and each time step individuals chose to visit fishing area $p$ (A, B and including area 0: “staying in port”), and to keep or discard any combination of the age classes caught of the quota species. This discarding was defined by a matrix $d$. The size of that matrix was defined by the number of species under quota constraints and the number of age classes. Each element could take the value 0 (discard) or 1 (keep on board and land). The expected utility for each state and each time step $s$ was calculated backward using stochastic dynamic programming \cite{ClarkandMangel2000}:
\begin{equation}
V (C_i, Q_i, F_i, s) = max_{p,d}( R(p, d, s)- G(p) - C(p) + E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1])),
\end{equation}
where $R(p, d, s)$ was the expected immediate contribution of the gross revenue from the sales of fish in a season resulting from choices $p$, and $d$ (gross revenues resulted from multiplying catches different age classes of species 1, species 2 and prices). Prices of fish were assumed to be dependent over fish age (subsection \ref{sec2.2.1}). $G(p)$ represented the incurred fuel costs per season from the choice of fishing area $a$, while  $ C(p)$ represented the variable operating costs (crew share, gear maintenance and landing costs, Table~\ref{t:fishery}), which in turn depended on the change in cumulative landings and fish prices. The term $E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1]$ denoted the expected future utility taken over all possible states resulting from choices $p$, and $d$. The transition of these states were based on normal distributions of catch rates, using the means and variances for the species, as explained in the model conditioning section, following \cite{Poos2010}.

@@

If $U^*$ was the expected utility at the optimal choice for a given t, we set
\begin{equation}
\Delta_{p, d}(C_i, Q_i, F_i, s) =  U^* (C_i, Q_i, F_i, s) - U (C_i, Q_i, F_i, s),
\end{equation}
and then defined the probability of a choice for a given area and discarding as	
\begin{equation} \label{eq:solve}
P_{p, d}(C_i, Q_i, F_i, s) = \frac
                % Nominator
                {e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}}
                % Denominator
                {\sum_p \sum_d e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}},
\end{equation}
where $\sigma$ was a tuning parameter that measures how important was to be near optimal. A high value of sigma resulted in uniform probabilities of choices, and that vessels were distributed uniformly among the different fishing areas. In contrast, if sigma was small then all vessels concentrated in the optimal location (but note that $\sigma$ should be $> 0$). For computations, we used $\sigma = 40$ (noting that $\Delta$ ranged from 0 to $\sim 2 x 10^{3}$, but was generally of the order of $1 x 10^2$ in magnitude).

@@

\begin{table}[!h]
\centering
\caption{Model and fishery conditioning.}
\label{t:fishery}
\resizebox{0.9\textwidth}{!}{%
\begin{tabular}{@{}lc lc lc @{}} 
\hline
\textbf{model}                              &               & \textbf{Fishery variable costs}                &      &\textbf{Fishery }&  \\ \hline
& & & \\%& & \\
number of vessels                           &700            &fuel costs (Euro day\textsuperscript{-1})       & 1240  & q                 & 0.0005 \\ 
$\sigma $                                   & 40            &gear maintenance (Euro day\textsuperscript{-1}) & 0    & effort (p,s)      & 1   \\
number of areas                             & 2             &crew share                                      & 35\% & CPUE & mean($pop*q*wts(yy-2:yy)$)\\
number of seasons                           & 6             &landing costs (Euro t\textsuperscript{-1})      & 0    & CPUE dev& $0.08*CPUE$\\
intial quota $Q_{sp1}$ and $Q_{sp2}$  & 200&                 &      \\%& & \\
& & & \\\hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependent pricing}
\label{sec2.2.1}
Prices of fish have been assumed to be fixed over time but influenced by the size of the catch. Common knowledge and case studies indicate that size and weight of a fish could be important attributes when determining its economic value \cite{Zimmermann2011, Zimmermann2013}. Therefore, the resulting data of mean weights and average prices were used for further analysis. We fitted linear mixed models, using mean price and mean body weight as the response variable and covariate, respectively. Thus, following \cite{Zimmermann2011}, the statistical models took the form:  
\begin{equation}
 pw_{i} \sim p_i \bar{w_i} + \beta_0 \times \frac{w_i-\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p$ is the mean price of species $i$, $\bar{w_i}$ is the mean weight of the corresponding weight classes, and the fraction corresponded to the standarization of the mass relative to the mean observed individual catch mass over all ages classes. $\beta_0$ gave the price increase when individial mass was increased by $\bar{w}$. We used mean prices of 150 Euro kg\textsuperscript{-1} for both species.
 %Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Linear mass-prices estimated based on mean prices per mass age-classes. The price slopes $\beta_0$ were assumed to be similar to mean prices.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}llcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
&                         & 1     & 2     & 3    & 4   \\ \hline
                      \\
Scenario I &              &       &        &       &     \\                       
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  778  & 1354   & 1780  & 2096  \\
                      \\
Scenario II &              &       &        &       &     \\ 
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  464  & 752    & 965   & 1123 \\
\\
\hline 
\end{tabular}
}
\end{table}

@@

\item
\textbf{Scenario I: Landings selectivity},  under this scenario the fishery is under landings selectivity, only landings contribute to yield. Fishing mortality accounts for all catches, regardless wether these catches are landed or discarded.

\item
\textbf{Scenario II: Fulll avoidance of discards}, this scenario contemplates the LO with landings selectivity only and fulll avoidance of discards.

@@

We simulated the effects of implementing a Management Plan (MP) and the Landing Obligation (LO) without any exceptions or flexibility. To be able to analyse the results of this complex actions of implementing the Mp and the LO, the implementations should start simultaneously for all stocks and fleets. Under the MP, the Harvest Control Rule for the TACs is to advise $F_{MSY}$ unless the biomass falls below a trigger biomass. If the biomass falls below this value, the advised TAC is based on the biomass trends. To check for trends, the latest biomass levels are compared to previous ones. If there is a decrease of a 20\% or more, the TAC is reduced by 15\%. If the comparision shows an increase of more then 20 \% the TAC is increased by 15\%.

\newpage
%\begin{landscape}
Scenario I: prices of the two species are equal (a truly mixed fishery)
%----------------------------------------------------------------------------------------------------------------------------------------
\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_scenarioI.eps} 
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_scenarioI.eps} 
\end{minipage}
\caption{}
\end{figure}
%\end{landscape}

Scenario II: prices of the species 2 are 50\% of species 1 prices
%----------------------------------------------------------------------------------------------------------------------------------------
\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_scenarioII.eps} 
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_scenarioII.eps} 
\end{minipage}
\caption{}
\end{figure}

\subsection{ catch decisions and location choice}
\label{sec3.1}
When discarding was allowed, but TACs changed by 15\% based on previous year but trying approximate to Fmsy, TACS showed a reduction and discards increased.

@@

@@

\newpage
\bibliographystyle{plain}
\bibliography{mylib}

>>>>

For purposes of model simplicity, we considered a hypothetical mixed fishery on two species. The fishery was modelled in a individual based dynamic state variable model. In order to allowed for fishing effort allocation, the model was seasonally (6 seasons) and spatially (areas A and B) explicit. The dynamics of the two fish species were governed by a simple age-structured model that is also seasonally and spatially explicit. The age structured model for the fish species was based on 4 cohorts, and individuals were assumed to be born at age 0, and in season 1. The number of fish $i$ of age $a$ at year $y$, in season $s$ and area $p$ was written as $N_i (a, y, s, p)$. The number of new-born individuals in the model was independent of the size of the adult population, but was function of area $p$ ($R_i (p)$). Numbers of recruits were set to 100 individuals during the first season, and spawning population of species 1 ocurred in area $A$, while species 2 did so in area B. Thus, individuals could be born in each of the areas, such that:

\begin{equation}
N_i (0, y, 1, p) = R_i (p)
\end{equation}

Moreover, combining the weight-based von Bertalanffy growth equation ($L\infty= 20$, $k= 0.093$), with the age-weight relationship ($W= L\infty*(1-e^{-k*a})$); weight per fish was higher for the older fish. Mortality in the model could occur from catches in the fishery, and natural causes such as predation, diseases, and scenesens. However, for simplicity we assumed that his natural mortality was negligible. Althought such absence of natural mortality impossible in reality, one could argue that the model thus mimics long-lived species. The decrease in population numbers was thus the result of the catches ($C_i (a, y, s, p)$), which were in turn a function of age dependent catchability $q(a)$, and fishing effort $E (y,s,p)$ in any time, season, and area.

\begin{equation}
C_i (a, y, s, p) = q(a) * E(y,s,p),
\end{equation}

and

\begin{equation}
N_i (a, y, s, p) = N_i (a, y, s, p) - C (a, y, s, p). 
\end{equation}

It was assumed that fishing mortality ocurred before migration ocurred. Migration for each species was defined by a matrix $M$ that defines the impact of migration (.e. immigration-emigration) on a given stock was also dependent on the relative sizes of the stocks. The size of that matrix  was defined by the number of age classes, seasons and number of immigrants into area $p$ ($im$) and emigrants leaving area $p$ ($em$) in the model. A 20 \% constant migration during any season was set between areas. The migration in population numbers ($Mig (a, 1, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs:

\begin{equation}
M (a, 1, s, im, em) = M (a, 1, s, im, em) + N (a, y, s, em) * P (a, y, s, i, em, im),
\end{equation}

and then population numbers

\begin{equation}
N (a, y, s, im) = N (a, y, s, im) +  M (a, 1, s, im, em).
\end{equation}

@@

To simulate the process of monitoring the stock, we developed models for state-dependent behaviour of individual fishing vessels, translated into behaviour of the fleet and implemented using stochastic dynamic programming \cite{Alzorriz2018, Batsleer2015, ClarkandMangel2000, Dowling2011, Houston1999, Poos2010}. A dynamic state variable model \cite{ClarkandMangel2000, Houston1999} was used to model location choice, extending the model structure in \cite{Batsleer2015}. In order to accommodate each individual vessels set of choices, the model may be constrained by individual vessels quota for the individual species and will respond by changing their fishing pattern in terms of: (i) whether or not to go fishing in one of the two areas ($A$ and $B$), and (ii) whether to discard one or more species and age class combinations. The model had annual fines for exceeding landings or catch quota as in \cite{Alzorriz2018}). In order to calculate state dependent choices during the year, we started by defining the annual fines for exceeding landings or catch quotas at the end of the year:
\begin{equation}
\Phi (C_i, Q_i, F_i)= -\sum_i (max( 0, (C_i - Q_i))* F_i),
\end{equation}

where $C_i$ was the cumulative annual landings or catches for species $i$ for an individual vessel. These cumulative landings defined the state of the individual. $Q_i$ was the annual individual quota for landings or catches for the quota species. Individual quotas were not transferable. In order to reduce computation time, we set quota only for two species. $F_i$ was the fine per unit weight for exceeding individual landings or catch quotas was set to $3 x 10^3$ Euro day\textsuperscript{-1}. These high fines combined with an assumed 100\% detection of exceeding quotas resulted in model results in which fishers comply with quota regulations.

The maximum expected utility between current season $s$ and the end of the year was $V (C_i, Q_i, F_i, s)$, and the model started by setting $V (C_i, Q_i, F_i, s)= \Phi (C_i, Q_i, F_i)$. For preceding seasons, the expected utility depended on individual choices, and each time step individuals chose to visit fishing area $p$ (A, B and including area 0: “staying in port”), and to keep or discard any combination of the age classes caught of the quota species. This discarding was defined by a matrix $d$. The size of that matrix was defined by the number of species under quota constraints and the number of age classes. Each element could take the value 0 (discard) or 1 (keep on board and land). The expected utility for each state and each time step $s$ was calculated backward using stochastic dynamic programming \cite{ClarkandMangel2000}:
\begin{equation}
V (C_i, Q_i, F_i, s) = max_{p,d}( R(p, d, s)- G(p) - C(p) + E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1])),
\end{equation}

where $R(p, d, s)$ was the expected immediate contribution of the gross revenue from the sales of fish in a season resulting from choices $p$, and $d$ (gross revenues resulted from multiplying catches different age classes of species 1, species 2 and prices). Prices of fish were assumed to be dependent over fish age (subsection \ref{sec2.2.1}). $G(p)$ represented the incurred fuel costs per season from the choice of fishing area $a$, while  $ C(p)$ represented the variable operating costs (crew share, gear maintenance and landing costs, Table~\ref{t:fishery}), which in turn depended on the change in cumulative landings and fish prices. The term $E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1]$ denoted the expected future utility taken over all possible states resulting from choices $p$, and $d$. The transition of these states were based on normal distributions of catch rates, using the means and variances for the species, as explained in the model conditioning section, following \cite{Poos2010}.

@@

If $U^*$ was the expected utility at the optimal choice for a given t, we set

\begin{equation}
\Delta_{p, d}(C_i, Q_i, F_i, s) =  U^* (C_i, Q_i, F_i, s) - U (C_i, Q_i, F_i, s),
\end{equation}

and then defined the probability of a choice for a given area and discarding as

\begin{equation} \label{eq:solve}
P_{p, d}(C_i, Q_i, F_i, s) = \frac
                % Nominator
                {e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}}
                % Denominator
                {\sum_p \sum_d e^{ -\Delta_{p, d}(C_i, Q_i, F_i, s)/\sigma}},
\end{equation}
where $\sigma$ was a tuning parameter that measures how important was to be near optimal. A high value of sigma resulted in uniform probabilities of choices, and that vessels were distributed uniformly among the different fishing areas. In contrast, if sigma was small then all vessels concentrated in the optimal location (but note that $\sigma$ should be $> 0$). For computations, we used $\sigma = 40$ (noting that $\Delta$ ranged from 0 to $\sim 2 x 10^{3}$, but was generally of the order of $1 x 10^2$ in magnitude).

@@

\begin{table}[!h]
\centering
\caption{Model and fishery conditioning.}
\label{t:fishery}
\resizebox{0.6\textwidth}{!}{%
\begin{tabular}{@{}lc@{}} 
\hline
\textbf{model}                              &               \\ \hline
&  \\%& & \\
number of vessels                           &700            \\ 
$\sigma $                                   & 40           \\
number of areas                             & 2            \\
number of seasons                           & 6            \\
intial quota $Q_{sp1}$ and $Q_{sp2}$        & 200 \\%& & \\
&  \\
\textbf{Fishery variable costs}             &               \\ \hline   
&  \\%& & \\
fuel costs (Euro day\textsuperscript{-1})       & 1240  \\ 
gear maintenance (Euro day\textsuperscript{-1}) & 0     \\ 
crew share                                      & 35\% \\ 
landing costs (Euro t\textsuperscript{-1})      & 0    \\ 
&                 \\  
\textbf{Fishery }&                 \\ \hline   
&  \\%& & \\
q                 & 0.0005 \\ 
effort (p,s)      & 1  \\ 
CPUE & mean($pop*q*wts(yy-2:yy)$)\\ 
CPUE dev& $0.08*CPUE$\\ 
&                 \\  \hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependent pricing}
\label{sec2.2.1}
Prices of fish have been assumed to be fixed over time but influenced by the size of the catch. Common knowledge and case studies indicate that size and weight of a fish could be important attributes when determining its economic value \cite{Zimmermann2011, Zimmermann2013}. Therefore, the resulting data of mean weights and average prices were used for further analysis. We fitted linear mixed models, using mean price and mean body weight as the response variable and covariate, respectively. Thus, following \cite{Zimmermann2011}, the statistical models took the form:  
\begin{equation}
 pw_{i} \sim p_i \bar{w_i} + \beta_0 \times \frac{w_i-\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p$ is the mean price of species $i$, $\bar{w_i}$ is the mean weight of the corresponding weight classes, and the fraction corresponded to the standarization of the mass relative to the mean observed individual catch mass over all ages classes. $\beta_0$ gave the price increase when individial mass was increased by $\bar{w}$. We used mean prices of 150 Euro kg\textsuperscript{-1} for both species.
 %Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Linear mass-prices estimated based on mean prices per mass age-classes. The price slopes $\beta_0$ were assumed to be similar to mean prices.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}lcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
                         & 1     & 2     & 3    & 4   \\ \hline
                      \\                      
species 1                &  778  & 1354   & 1780  & 2096  \\
species 2                &  778  & 1354   & 1780  & 2096  \\

\\
\hline 
\end{tabular}
}
\end{table}

@@

\item
\textbf{MP Scenario: Landings selectivity},  under this scenario the fishery is under landings selectivity, only landings contribute to yield. Fishing mortality accounts for all catches, regardless wether these catches are landed or discarded.

\item
\textbf{LO Scenario: Fulll avoidance of discards}, this scenario contemplates the LO with landings selectivity only and fulll avoidance of discards.

@@

We simulated the effects of implementing a Management Plan (MP) and the Landing Obligation (LO) without any exceptions or flexibility. To be able to analyse the results of this complex actions of implementing the MP and the LO, the implementations should start simultaneously for all stocks and fleets. Under the MP, the Harvest Control Rule for the TACs is to advise $F_{MSY}$ unless the biomass falls below a trigger biomass. If the biomass falls below this value, the advised TAC is based on the biomass trends. To check for trends, the latest biomass levels are compared to previous ones. If there is a decrease of a 20\% or more, the TAC is reduced by 15\%. If the comparision shows an increase of more then 20 \% the TAC is increased by 15\%.

\subsection{Catch decisions and location choice}
\label{sec3.1}
When discarding was allowed, but TACs changed by 15\% based on previous year but trying approximate to Fmsy, TACS showed a reduction and discards increased.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/figurecatches.eps} 
\caption{Caches and harvest rates- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/figurecatches2.eps} 
\caption{Change in selectivity- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.82\textwidth]{Figures/figureffort.eps} 
\caption{Effort- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/figurerevenue.eps} 
\caption{Revenues- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}
%---

@@

\bibliographystyle{plain}
\bibliography{mylib}

\newpage
\begin{notes}[Apendix]

Different scenarios, considering wether prices of the two species are equal or not.

\begin{table}[!h]
\centering
\caption{Linear mass-prices estimated based on mean prices per mass age-classes. The price slopes $\beta_0$ were assumed to be similar to mean prices.}
\label{t:pricing}
\resizebox{0.8\textwidth}{!}{%
\begin{tabular}{@{}llcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
&                         & 1     & 2     & 3    & 4   \\ \hline
                      \\
Scenario I &              &       &        &       &     \\                       
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  778  & 1354   & 1780  & 2096  \\
                      \\
Scenario II &              &       &        &       &     \\ 
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  621  & 1053    & 1373   & 1610 \\
                      \\
Scenario III &              &       &        &       &     \\ 
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  464  & 752    & 965   & 1123 \\
                      \\
Scenario IV &              &       &        &       &     \\ 
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  307  & 451    & 558   & 637 \\

\\
\hline 
\end{tabular}
}
\end{table}

%----------------------------------------------------------------------------------------------------------------------------------------
\newpage
\begin{landscape}
\begin{figure}[!h]
\centering
\includegraphics[.45\textwidth]{Figures/Catch_scenarioI.eps} 
\includegraphics[.45\textwidth]{Figures/Effort_scenarioI.eps}
\caption{Scenario I: Prices of the two species are equal (a truly mixed fishery)}
\end{figure}
\end{landscape}

\newpage
\begin{landscape}
\begin{figure}[!h]
\centering
\includegraphics[.45\textwidth]{Figures/Catch_scenarioII.eps} 
\includegraphics[.45\textwidth]{Figures/Effort_scenarioII.eps}
\caption{Scenario II: prices of the species 2 are 75\% of species 1 prices)}
\end{figure}
\end{landscape}

\newpage
\begin{landscape}
\begin{figure}[!h]
\centering
\includegraphics[.45\textwidth]{Figures/Catch_scenarioIII.eps} 
\includegraphics[.45\textwidth]{Figures/Effort_scenarioIII.eps}
\caption{Scenario III: prices of the species 2 are 50\% of species 1 prices)}
\end{figure}
\end{landscape}

\newpage
\begin{landscape}
\begin{figure}[!h]
\centering
\includegraphics[.45\textwidth]{Figures/Catch_scenarioIV.eps} 
\includegraphics[.45\textwidth]{Figures/Effort_scenarioIV.eps}
\caption{Scenario IV: prices of the species 2 are 25\% of species 1 prices)}
\end{figure}
\end{landscape}

%\begin{figure}[!h]
%\centering
%\begin{minipage}{.45\textwidth}
%\includegraphics[width=0.9\textheight]{Figures/Catch_scenarioII.eps} 
%\end{minipage}
%\hfill
%\begin{minipage}{.45\textwidth}
%\includegraphics[width=0.9\textheight]{Figures/Effort_scenarioII.eps} 
%\end{minipage}
%\caption{Scenario II: prices of the species 2 are 50\% of species 1 prices}
%\end{figure}

\end{notes}
